\documentclass[10pt, letterpaper]{article}

%
% PACKAGES
%
\usepackage[
    ignoreheadfoot,
    top=2cm,
    bottom=2cm,
    left=2cm,
    right=2cm,
    footskip=1.0cm,
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Praval Parikh},
    pdfauthor={Praval Parikh},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}

%
% PDF-SPECIFIC CONFIG
%
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

%
% CUSTOM COLORS & FONTS
%
\definecolor{primaryColor}{RGB}{0, 79, 144}

%
% LAYOUT & STYLE
%
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.5cm}

% Section title formatting (compact)
\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{0pt}{0.3cm}{0.2cm} % left, before, after (reduced from 0.4cm/0.3cm)

% Custom command for consistent project spacing (compact)
\newcommand{\projectsep}{\vspace{0.15cm}} % (reduced from 0.3cm)

% Custom command for contact info separator
\newcommand{\contactseparator}{\kern 0.1cm \color{gray!70} | \kern 0.1cm}

% Hyperlink formatting (removes default arrow)
\let\hrefWithoutArrow\href
\renewcommand{\href}[2]{\hrefWithoutArrow{#1}{\ifthenelse{\equal{#2}{}}{ }{#2 }\raisebox{.15ex}{\footnotesize \faExternalLink*}}}

%
% CUSTOM ENVIRONMENTS
%
% Highlights environment (list with compact spacing)
\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.1cm,
        parsep=0.05cm,
        partopsep=0pt,
        itemsep=0cm, % (reduced from 0.05cm)
        leftmargin=0.4cm + 10pt
    ]
}{
    \end{itemize}
}

% Entry for a single column
\newenvironment{onecolentry}{
    \begin{adjustwidth}{0.2cm}{0.2cm}
}{
    \end{adjustwidth}
}

% Entry for two columns (e.g., Title on left, Date/Link on right)
\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

% Header environment
\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.4} % (linespread reduced from 1.5)
}{
    \par\kern\topsep
}


\begin{document}

%
% HEADER
%
\begin{header}
    \textbf{\fontsize{24pt}{24pt}\selectfont Praval Hitesh Parikh}

    \vspace{0.15cm} % (reduced from 0.2cm)
    \small
    \mbox{\hrefWithoutArrow{mailto:praval.parikh@gmail.com}{\color{black}{\faEnvelope[regular]}\hspace*{0.13cm}praval.parikh@gmail.com}}
    \contactseparator
    \mbox{\hrefWithoutArrow{tel:+91-74900-42418}{\color{black}{\faPhone*}\hspace*{0.13cm}7490042418}}
    \contactseparator
    \mbox{\hrefWithoutArrow{https://www.linkedin.com/in/praval-parikh/}{\color{black}{\faLinkedinIn}\hspace*{0.13cm}linkedin.com/in/praval-parikh}}
    \contactseparator
    \mbox{\hrefWithoutArrow{https://github.com/Plebsicle}{\color{black}{\faGithub}\hspace*{0.13cm}github.com/Plebsicle}}
\end{header}

%
% SUMMARY
%
\section{Summary}
\begin{onecolentry}
    \textit{CSE undergraduate with a strong foundation in backend systems and distributed architectures. Passionate about building reliable software through clean design, testing, and automation.}
\end{onecolentry}




%
% EDUCATION
%
\section{Education}
\begin{twocolentry}{\textbf{Gandhinagar, India} \\ }
    \textbf{Indian Institute of Information Technology Vadodara}

    \textit{B.Tech in Computer Science \& Engineering}
\end{twocolentry}

\begin{onecolentry}
    \begin{highlights}
        \item Cumulative GPA: 8.36 / 10.0
        \item Relevant Coursework: Data Structures & Algorithms, DBMS, SWE
    \end{highlights}
\end{onecolentry}

%
% PROJECTS
%
\section{Projects}

\begin{twocolentry}{\textit{\href{https://github.com/Plebsicle/feature-flags}{GitHub Link}} \textbar \textit{\href{https://bitswitch.tech}{Live}}}
    \textbf{Feature Flag Management System}
\end{twocolentry}
\begin{onecolentry}
    \begin{highlights}
        \item Built a feature flag service with real-time SDK-based evaluation, custom rollout rules, and environment isolation.
        \item Used Redis caching for low-latency evaluation and PostgreSQL for persistent rule storage.
        \item Enabled Slack alerts, kill switch functionality, and environment-level metrics for production observability.
        \item Secured APIs with role-based access control and session management.
        \item Developed a responsive admin dashboard using Next.js and Tailwind for managing flags and usage insights.
        \item Written unit tests using Vitest with mocked Redis and database clients, helping catch critical bugs in
evaluation and rollout logic; planning CI/CD integration for automated test workflows.

        \item \textbf{Tech Stack:} TypeScript, Node.js, Express, PostgreSQL, Redis, Next.js, Tailwind
    \end{highlights}
\end{onecolentry}






\projectsep

\begin{twocolentry}{\textit{\href{https://github.com/Plebsicle/microfin}{GitHub Link}}}
    \textbf{Scalable Financial Transactions System}
\end{twocolentry}
\begin{onecolentry}
    \begin{highlights}
        \item Architected a distributed backend capable of 3,600+ RPS with strong ACID guarantees using PostgreSQL + PgBouncer.
        \item Leveraged Kafka for asynchronous processing with deduplication, idempotency, and failure recovery.
        \item Used Redis for atomic balance updates and real-time caching to reduce DB pressure.
        \item Introduced worker hashing for concurrency control and integrated monitoring via Prometheus and Grafana.
        \item Load tested the system under concurrent pressure using K6 to validate throughput and latency.
        \item Unit tests written using Vitest with mocked Redis and database clients, helping identify edge-case bugs and consistency issues during development.
        \item \textbf{Tech Stack:} TypeScript, PostgreSQL, Kafka, Redis, NGINX, Docker, Prometheus, Grafana
    \end{highlights}
\end{onecolentry}




\projectsep

\begin{twocolentry}{\textit{\href{https://github.com/Plebsicle/Medication-Management}{GitHub Link}} \textbar \textit{\href{https://medman.app}{Live}}}
    \textbf{Medication Management System}
\end{twocolentry}
\begin{onecolentry}
    \begin{highlights}
        \item Built a full-stack system for tracking medications and scheduling SMS/email reminders using Twilio.
        \item Enabled secure medical document upload via AWS S3 presigned URLs and OAuth2-based login.
        \item Integrated OpenAI API to build a chatbot for answering patient queries from within the app.
        \item \textbf{Tech Stack:} TypeScript, Node.js, Express, PostgreSQL, Redis, React.js, Tailwind, AWS S3
    \end{highlights}
\end{onecolentry}





%
% TECHNICAL SKILLS
%
\section{Technical Skills}
\begin{onecolentry}
\textbf{Languages:} JavaScript, TypeScript, SQL, C++ \\
\textbf{Tools/Frameworks:} Node.js, Express, Redis, PostgreSQL, Kafka, Docker, Prometheus, Vitest, K6 \\
\textbf{Frontend:} React, Tailwind CSS \\
\textbf{Other:} Git, GitHub, Postman, GitHub Actions, REST APIs
\end{onecolentry}


%
% ACHIEVEMENTS
%
\section{Achievements}
\begin{onecolentry}
    \begin{highlights}
        \item Solved 400+ problems on Codeforces with a peak rating of 1296 (Pupil).
        \item Solved 300+ problems on LeetCode across various difficulty levels.
    \end{highlights}
\end{onecolentry}

\end{document}